Adaptive Safe Strong Screening for Efficient Lasso-Type Problems Optimization over the Solution Path

### 2021-01-19 main.tex

The SEDPP rule \eqref{eq:sedpp} from Theorem 2.2 allows us to screen features at $\lambda_{k+1}$ using the solution at $\lambda_k$ as a reference. However, since the grid of $\lam$ values is arbitrary, the rule with the same reference can be just as easily applied to screen solutions at $\lam_{k+2}, \lam_{k+3}, \ldots$, until some $\lam_{k+B}$, where we update the reference to the current solution at $\lam_{k+B}$ and screen the following $\lam$ values.  The difference is that in typical SEDPP usage, we would update the reference solution at every step of path; here, we are proposing to re-use solutions for several values of $\lam$, only updating the reference when it is computationally beneficial to do so.  We refer to this modification as \emph{adaptive EDPP}.  Adaptive EDPP is still a safe rule, but it is neither sequential nor one-step.  A similar idea would be to use the reference solution in batches, each one being used for a fixed number of $\lam$ steps.  However, since an appropriate batch size is difficult to determine ahead of time, and also because the ideal size changes along the path, we find that an adaptive approach is better (see Section~\ref{sec:adaptive}).

The Adaptive EDPP rule can be stated in the following theorem, which simply restates the theorems from Section~\ref{sec:safe} in terms of this new paradigm in which a single reference solution at $\lam_k$ is used to calculate screening rules at $\lam_{k+1}, \ldots, \lam_{k+B}$.

>>>>

The SEDPP rule \eqref{eq:sedpp} from Theorem 2.2 allows us to screen features at $\lambda_{k+1}$ using the solution at $\lambda_k$ as a reference. However, since the grid of $\lam$ values is arbitrary, the rule with the same reference can be just as easily applied to screen solutions at $\lam_{k+2}, \lam_{k+3}, \ldots$, until some $\lam_{k+B}$, where we update the reference to the current solution at $\lam_{k+B}$ and screen the following $\lam$ values.  The difference is that in typical SEDPP usage, we would update the reference solution at every step of path; here, we are proposing to re-use solutions for several values of $\lam$, only updating the reference when it is computationally beneficial to do so.  We refer to this modification as \emph{adaptive EDPP}.  Adaptive EDPP is still a safe rule, but it is neither sequential nor one-step.  A similar idea would be to use the reference solution in batches, each one being used for a fixed number of $\lam$ steps.  However, since an appropriate batch size is difficult to determine ahead of time, and also because the ideal size changes along the path, we find that an adaptive approach is better as we will show in \ref{sec:complexity}.
The Adaptive EDPP rule can be stated in the following theorem, which simply restates the theorems from Section~\ref{sec:safe} in terms of this new paradigm in which a single reference solution at $\lam_k$ is used to calculate screening rules at $\lam_{k+1}, \ldots, \lam_{k+B}$.
